


\documentclass[]{main}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Abdulrahman}{Mosaibah}{ \urlstyle{same}\href{http://debarghyadas.com}{debarghyadas.com}| \href{http://fb.co/dd}{fb.co/dd}\\
\href{mailto:abudrm2020@gmail.com}{abudrm2020@gmail.com} | 0544986623 | 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Bahrain}
\descript{BS in Software Engineering}
\location{Expected Graduation in Jun 2024}
Bahrain | College of IT
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/mosaibah}{\bf Mosaibah} \\
LinkedIn://  \href{https://www.linkedin.com/in/Abdulrahman-Mosaibah}{\bf Abdulrahman} \\
Twitter://  \href{https://twitter.com/proAbdulrahmna}{\bf @ProAbdulrahman} \\
YouTube://  \href{https://www.youtube.com/@abdulrahman-mosaibah}{\bf Abdulrahman} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{TECHNOLOGIES SKILLS}
\vspace{\topsep}
\location{Programming Languages:}
C \# \textbullet{}   Javascript \textbullet{} PHP \\ 
\vspace{\topsep}
\location{Other Technologies:}
ASP .NET CORE \textbullet{} Laravel \textbullet{} DBMS \textbullet{} Linux(Ubountu, CentOS) \textbullet{} SQL( MS SQL Server, MySQL, PostgreSQL  \textbullet{} Digitalocean  \textbullet{} Git \& GitHub \textbullet{} React.js \textbullet{} Bootstrap \textbullet{} TailwndCss \textbullet{} HTML \textbullet{} CSS \textbullet{} Retool \textbullet{} Metabase \textbullet{} \LaTeX 

\sectionsep

blogs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Moya App}
\descript{| Software Engineer }
\location{Nov 2021 - Present | 1 yr 3 mos | Part Time}
\vspace{\topsep}
\begin{tightemize}
\item MoyaApp is a platform that connects consumers of water and beverages with the majority of distributors and suppliers in the Kingdom.
\item Re-built MoyaApp's dashboard from scratch (ASP .Net). 
\item Writing business logic (Logistic, E-commerce and Operation)
\item Developed server-side \& client-side pagination, Authentication \& Authorization, and used Entity Framework Core.
\item Worked with developers to design algorithms, database schema, and flowcharts.
\item Developed SQL queries, and views for reporting and made it automated using Metabase.
\item Stack: ASP .NET Core, Javascript, Bootstrap, MS SQL Server and PostgreSQL.
\end{tightemize}
\sectionsep


\runsubsection{Masader}
\descript{| Open Source Contributor  }
\location{ Jul 2022 - Aug 2022 }
\begin{tightemize}
\item The first online catalogue for Arabic NLP datasets. This catalogue contains 606 datasets with more than 25 metadata annotations for each dataset.
\item Improving the front-end codebase and adding features. 
\item Link to \href{https://github.com/ARBML/masader/pull/89}{\underline{\emph{my contribution}}}
\item Link to the \href{https://arxiv.org/pdf/2208.00932.pdf}{\underline{\emph{research paper}}}

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Side Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Side Projects}

\runsubsection{Meshkah}
\descript{| Creator  }
\location{ Jan 2023 - Present }
\begin{tightemize}
\item Meshkah is a web application that aim to manage points of students etc etc.
\item Improving the front-end codebase and adding features. 
\item Deployed teh app on Digitalocean
\item Stack: ASP .NET CORE MVC, PostegrSQL and Bootstrap 
\item Link to \href{http://Meshkah.Mosaibah.com}{\underline{\emph{Demo}}}
\item Link to \href{https://github.com/Mosaibah/Meshkah}{\underline{\emph{GitHub Repository}}}
\end{tightemize}
\sectionsep

\runsubsection{Amazon Clone}
\descript{| Creator  }
\location{ Sep 2021 - Oct 2021 }
\begin{tightemize}
\item Cloning Amazon website.
\item Improving the front-end codebase and adding features. 
\item Deployed teh app on Digitalocean
\item Stack: React.js, Bootstrap and Firebase
\item Link to \href{https://clone-72059.web.app/}{\underline{\emph{Demo}}}
\item Link to \href{https://github.com/Mosaibah/amazon-clone}{\underline{\emph{GitHub Repository}}}
\end{tightemize}
\sectionsep


\runsubsection{Tahdani}
\descript{| Creator  }
\location{ Jan 2021 - Mar 2021 }
\begin{tightemize}
\item Tahadani is a quiz creator.
\item etc etc. 
\item Stack: PHP, Javascript, HTML, CSS and Bootstrap
\item Link to \href{https://github.com/Mosaibah/quiz-creator}{\underline{\emph{GitHub Repository}}}
\end{tightemize}
\sectionsep

% \runsubsection{Restaurant Menu}
% \descript{| Creator  }
% \location{ Mar 2021 - Jul 2021 }
% \begin{tightemize}
% \item CRUD Website.
% \item etc etc. 
% \item Stack: Laravel, Javascript and Bootstrap
% \item Link to \href{https://github.com/Mosaibah/restaurantapp/commits/master}{\underline{\emph{GitHub Repository}}}
% \end{tightemize}
% \sectionsep




\end{minipage} 
\end{document}  \documentclass[]{article}
